### 2018-05-22 Paper/examples.tex
..

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/sense_borehole}
  \includegraphics[width=0.51\textwidth]{./Figures/ub_conv_borehole}
\caption{
Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the
borehole discharge function in~\eqref{eq:bore}. Right: 
Estimates of the screening parameter ($\widehat{\mathcal{C}_i\mu_i}$), plotted
against number of samples. Also included in the legend are estimates of $\mathcal{T}(\theta_i)$
in each case in the legend.}
\label{fig:sense_bore}
\end{center}
\end{figure}

@@

Converged estimates of $\mathcal{T}(\theta_i)$ are once again obtained easily by
evaluating $g(\bm{X})$ for a large set of samples in the uncertain 
parameter space; see Figure~\ref{fig:sense_osc}~(left). Estimates of the screening metric, 
$\widehat{\mathcal{C}_i\mu_i}$ are plotted against the number of samples in 
Figure~\ref{fig:sense_osc}~(right). 
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/sense_oscillator}
  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_oscillator}
\caption{
Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the limit 
state function in~\eqref{eq:limit}. Right: 
Estimates of the screening parameter ($\widehat{\mathcal{C}_i\mu_i}$), plotted
against number of samples. Also included in the legend are estimates of $\mathcal{T}(\theta_i)$
in each case in the legend.}
\label{fig:sense_osc}
\end{center}
\end{figure}
We note that the total Sobol sensitivity indices are in excellent agreement
with the screening metric estimates. 
Consequently, the parameter ranks are found to be consistent in the
two plots in  
Figure~\ref{fig:sense_osc}.
It is observed that the limit state function is predominantly sensitive 
to $r$, $F$, and $t_1$. Hence, it seems likely that an ROS in
three dimensions is able to capture the overall uncertainty in $g(\bm{X})$.
% due to uncertainty in the six parameters. 
To illustrate computational gains as a
result of dimension-reduction, we construct PCEs in 3D, 4D (accounts for the
uncertainty in $k_1$ as well), and the original 6D parameter domain. In
Figure~\ref{fig:conv_osc}~(left), we compare the convergence of the
PCEs. As expected, the third-order PCE converges much faster than the other
two. Consequently, the number of model evaluations required for a converged PCE
is expected to be relatively much smaller in this case.  
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_oscillator}
  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_oscillator}
\caption{Left: Logarithm of $\epsilon_{\mbox{\tiny{LOO}}}$ is against sample size for 
PCEs constructed in 3, 5, and 6 dimensions to compare their convergence characteristics. 
Right: PDF of the limit state function is plotted using the actual function in~\eqref{eq:limit}
and the third-order PCE.}
\label{fig:conv_osc}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.6\textwidth]{./Figures/u_soln}
  \caption{Plotted above is the solution, $u(x,y)$ of~\eqref{eq:semilinear} at fixed values
  of $\kappa$, $c$, and $\alpha_i$ as provided. The color-bar indicates the range of $u$.}
\label{fig:usoln}
\end{center}
\end{figure}

%We consider the semilinear elliptic PDE,
%\begin{equation}\label{equ:semilinear}
%\begin{aligned}
%-\kappa \Delta u + c u^3 &= q, \quad \text{in } \Omega\\
% u &= 0. \quad \text{on } \partial \Omega
%\end{aligned}
%\end{equation}
%We model the source term as 
%\begin{equation}
%q(x, y, \theta) = \sum_{i = 1}^N \theta_i \sin(i \pi x)
%\cos(i \pi y),
%\quad N = 8.
%\end{equation}
%Here $\kappa \sim U(0.08, 0.12)$, $c \sim U(0.8, 1.2)$, 
%and $\theta_i$ are uniformly distributed in interval $[0, 1]$. We consider
%the following QoI,
%\[
%     f(\kappa, c, \theta) = \frac{1}{|D|} \int_D u(x; \kappa, c, \theta) \, dx, 
%\]
%where $D$ is the region, $[1/2, 3/4] \times [1/2, 3/4]$.

>>>>

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/sense_borehole}
  \includegraphics[width=0.51\textwidth]{./Figures/ub_conv_borehole}
\caption{
Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the
borehole discharge function in~\eqref{eq:bore}. Right: 
Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), plotted
against number of samples. Also included in the legend are estimates of $\mathcal{T}(\theta_i)$
in each case in the legend.}
\label{fig:sense_bore}
\end{center}
\end{figure}

@@

Converged estimates of $\mathcal{T}(\theta_i)$ are once again obtained easily by
evaluating $g(\bm{X})$ for a large set of samples in the uncertain 
parameter space; see Figure~\ref{fig:sense_osc}~(left). Estimates of the screening metric, 
$\widehat{\mathcal{C}_i\mu_i}$ are plotted against the number of samples in 
Figure~\ref{fig:sense_osc}~(right). 
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/sense_oscillator}
  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_oscillator}
\caption{
Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the limit 
state function in~\eqref{eq:limit}. Right: 
Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$), plotted
against number of samples. Also included in the legend are estimates of $\mathcal{T}(\theta_i)$
in each case in the legend.}
\label{fig:sense_osc}
\end{center}
\end{figure}
We note that the total Sobol sensitivity indices are in excellent agreement
with the screening metric estimates. 
Consequently, the parameter ranks are found to be consistent in the
two plots in  
Figure~\ref{fig:sense_osc}.
It is observed that the limit state function is predominantly sensitive 
to $r$, $F$, and $t_1$. Hence, it seems likely that an ROS in
three dimensions is able to capture the overall uncertainty in $g(\bm{X})$.
% due to uncertainty in the six parameters. 
To illustrate computational gains as a
result of dimension-reduction, we construct PCEs in 3D, 4D (accounts for the
uncertainty in $k_1$ as well), and the original 6D parameter domain. In
Figure~\ref{fig:conv_osc}~(left), we compare the convergence of the
PCEs. As expected, the third-order PCE converges much faster than the other
two. Consequently, the number of model evaluations required for a converged PCE
is expected to be relatively much smaller in this case.  
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_oscillator}
  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_oscillator}
\caption{Left: Logarithm of $\epsilon_{\mbox{\tiny{LOO}}}$ is plotted against sample size for 
PCEs constructed in 3, 5, and 6 dimensions to compare their convergence characteristics. 
Right: PDF of the limit state function is plotted using the actual function in~\eqref{eq:limit}
and the third-order PCE.}
\label{fig:conv_osc}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.6\textwidth]{./Figures/u_soln}
  \caption{Plotted above is the solution, $u(x,y)$ of~\eqref{eq:semilinear} at 
  of $\kappa$~=~0.075, $c$~=~1.5, and $\alpha_i$~=~4.0.}
\label{fig:usoln}
\end{center}
\end{figure}

We aim to construct a reduced-order surrogate for the following quantity of interest (QoI):

\be
\mathcal{F}(\kappa, c, \theta) = \frac{1}{|D|} \int_D u(x; \kappa, c, \theta) \, dx, 
\label{eq:qoi}
\ee
%
where $D$ is the region: $[2/5, 3/5] \times [2/5, 3/5]$. Once again, the availability of
cheap model evaluations allow us to obtain converged estimates of the Sobol
total-effect index ($\mathcal{T}(\theta_i)$), plotted in Figure~\ref{fig:sense_elliptic}.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.46\textwidth]{./Figures/sense_elliptic}
  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_elliptic}
\caption{
Left: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the 
semi-linear elliptic PDE~\eqref{eq:semilinear}. Right: 
Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$) for each uncertain parameter,
obtained using $N$ = 5, 10, 15, and 20 samples in the full parameter space.}
\label{fig:sense_elliptic}
\end{center}
\end{figure}
%
Sensitivity predictions based on the screening metric, $\widehat{\mathcal{C}_i\mu_i}$ are found to
be in close agreement with $\mathcal{T}(\theta_i)$, even for the case when $N$ = 5. Moreover, 
the uncertainty in the QoI in \eqref{eq:qoi} is observed to be largely dependent on $c$, 
$\alpha_2$, $\alpha_3$, $\alpha_4$, and $\alpha_5$. These observations underscore the
potential for computational gains by constructing an ROS in the 5D parameter space. We 
illustrate the comparison of convergence characteristics of the PCEs constructed in the
full parameter space (10D) and the reduced space (5D) in Figure~\ref{fig:conv_elliptic} (left). 
As expected, the ROS converges at a much faster rate. Using model evaluations at 90
sample points, $\epsilon_{\mbox{\tiny{LOO}}}$ is found to be two orders of magnitude
smaller than that in the case of full-surrogate ($\mathcal{O}(10^{-4}$) vs. $\mathcal{O}(10^{-2}$)). 
Consequently, the computational effort for constructing the ROS in the present test problem
is expected to be much smaller.

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/err_samples_elliptic}
  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_elliptic}
\caption{Left: Logarithm of $\epsilon_{\mbox{\tiny{LOO}}}$ is plotted against sample size for 
PCEs constructed in 10 and 5 dimensions to compare their convergence characteristics. 
Right: PDF of the QoI, $\mathcal{F}(\kappa, c, \theta)$ in~\eqref{eq:semilinear} is
plotted using the full-surrogate and the reduced-order PC surrogate.}
\label{fig:conv_elliptic}
\end{center}
\end{figure}
